---
title: "DS in Context Lift Curve"
author: "Thomas Hill"
date: "3/18/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Generating Lift Curves 

Using the example from the Caret package in R, found here <http://topepo.github.io/caret/>, I was able to generate some predicted data to visualize. Below is the code generating the the predictions, based on three methods: FDA (Flexible Discriminant Analysis), LDA (Linear Discriminant Analysis), and the C5.0 model.

```{r caret-example-data}
set.seed(2)
lift_training <- twoClassSim(1000)
lift_testing  <- twoClassSim(1000)

ctrl <- trainControl(method = "cv", classProbs = TRUE,
                     summaryFunction = twoClassSummary)

set.seed(1045)
fda_lift <- train(Class ~ ., data = lift_training,
                  method = "fda", metric = "ROC",
                  tuneLength = 20,
                  trControl = ctrl)
set.seed(1045)
lda_lift <- train(Class ~ ., data = lift_training,
                  method = "lda", metric = "ROC",
                  trControl = ctrl)

library(C50)
set.seed(1045)
c5_lift <- train(Class ~ ., data = lift_training,
                 method = "C5.0", metric = "ROC",
                 tuneLength = 10,
                 trControl = ctrl,
                 control = C5.0Control(earlyStopping = FALSE))

## Generate the test set results
lift_results <- data.frame(Class = lift_testing$Class)
lift_results$FDA <- predict(fda_lift, lift_testing, type = "prob")[,"Class1"]
lift_results$LDA <- predict(lda_lift, lift_testing, type = "prob")[,"Class1"]
lift_results$C5.0 <- predict(c5_lift, lift_testing, type = "prob")[,"Class1"]
head(lift_results)
```

# Generating Lift Curves of the Three Methods

Now that I have some simulated data, I can plot the results of the three classifiers against each other. The resulting graph is the cumulative response curve.

```{r cumulative-response-curve}

library(caret)
trellis.par.set(caretTheme())
lift_obj <- lift(Class ~ FDA + LDA + C5.0, data = lift_results)
plot(lift_obj, values = 60, auto.key = list(columns = 3,
                                            lines = TRUE,
                                            points = FALSE))
```



